Beyond Capacity: Analyzing Shelter Use and Government Responses to Homelessness in Toronto

### 2024-03-15 paper/paper.qmd
new update.........

>>>>

```{r}
#| label: fig-across_cities
#| fig-cap: Occupancy of Shelter Rooms by Sector Across Toronto Cities
#| echo: false
#| warning: false
#| message: false
toronto_shelters_clean |>
  drop_na(occupied_rooms, sector, location_city) |>
  ggplot(aes(x = location_city, y = occupied_rooms, color = sector)) +
  geom_point() +
  theme_minimal() +
  labs(x = "location_city", y = "occupied_rooms", color = "Sector") +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```
